Disk Heating, Galactoseismology, and the Formation of Stellar Halos

### 2017-06-18 paper/paper_v1.tex
a few more comments

% APW COMMENT: I think your reference "jurie17" should be "lurie17" -- maybe
% combined John Lurie's last name with Mario Juric's?

\usepackage{microtype}  % ALWAYS!
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsrefs}
\usepackage{aas_macros}

@@

Emerging in the 1990's, the catalogues that inspired this recent acceleration not only mapped global structures in our Galaxy, but also revealed the ubiquity of substructure within it.
These revelations added an unforeseen richness to interpretations, and encouraged the development of new dynamical tools for studying ongoing interactions and formation histories:
\survey{Hipparcos} \citep{esa97} found moving groups of stars in the velocity distribution in the Solar Neighborhood \citep{dehnen98}, some corresponding (as expected) to destroyed stars clusters, while others (unexpectedly) could plausibly be explained as signatures of resonances with the Galactic bar \citep{dehnen00};
the Sloan Digital Sky Survey \citep[hereafter, SDSS ---][]{york00,stoughton02,abazajian03} found many streams of Main Sequence Turnoff (MSTO) stars in our stellar halo, thought to be from long-dead satellite galaxies and dissolved globular clusters \citep{newberg02,belokurov06} as a stunning confirmation that our Galaxy had indeed formed hierarchically \citep[e.g.][]{bullock01,bullock05};
and M giant stars selected from the Two Micron All Sky Survey \citep[hereafter, 2MASS ---][]{nikolaev00} traced the debris from the Sagittarius dwarf galaxy entirely around the Sky \citep{majewski03} to offer a window on the history of its disruption \citep{law10}.
From these and many other studies that use large survey catalogues, it is now clear that the Milky Way is full of kinematic substructure.
% APW COMMENT: this section makes it sound like the surveys discovered these things "for free," but really it was the authors you cite who found these things. I would rearrange to say, e.g., "Using data from the \survey{Hipparcos} mission \citep{esa97}, moving groups of stars were found in the velocity distribution in the Solar Neighborhood \citep{dehnen98}...etc"

@@

% APW COMMENT: If the sections are reorganized to be by structure instread,
% this could get moved to the discussion. "Discussion: connections to velocity
% structure near the Sun" or something

@@

Co-incidental with the above spectroscopic and stellar populations work, \cite{xu15} and \cite{jurie17} explored the spatial distribution of stars in the anticenter region using photometry in the SDSS and PanSTARRS \citep{kaiser10} respectively.
Both employed the novel technique of subtracting color-magnitude diagrams (CMD's) derived from fields in their photometric data which were symmetrically placed at equal and opposite Galactic latitudes and at the same Galactic longitudes.
These differenced CMD's showed sequences in overdensities oscillating between the northern and southern hemispheres as the distance from the Sun was increased towards the anticenter of our Galaxy.
The vast numbers of stars in these surveys allowed more clear identification of the global structures as clearly distinct, separate features.

@@

@@

Figure \ref{fig:cartoon} is a cartoon which summarizes the observational work and its implications, by showing the approximate locations and amplitudes of the spatial and velocity structures that have been identified. (Note that the figure is misleading as the structures are {\it not} consistent morphologically with concentric rings that are axisymmetric about the Galactic center.)
Taken together, we conclude: (i) there is compelling evidence that Mon/GASS, TriAnd I/II and A13 represent populations of stars formed in the disk that now exist at extreme $(R,Z)$;
(ii) that these structures are associated with each other as part of a global system of vertical disk oscillations that can be traced all the way to the velocity asymmetries seen in the Solar Neighborhood; and
(iii) that the stellar populations in these structures are inconsistent with a picture where they formed from an accreted satellite.

>>>>

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsrefs}
% \usepackage{aas_macros} % APW: I needed this for the references...

@@

Emerging in the 1990's, the catalogues that inspired this recent acceleration not only mapped global structures in our Galaxy, but also revealed the ubiquity of substructure within it.
These revelations added an unforeseen richness to interpretations, and encouraged the development of new dynamical tools for studying ongoing interactions and formation histories:
\survey{Hipparcos} \citep{esa97} found moving groups of stars in the velocity distribution in the Solar Neighborhood \citep{dehnen98}, some corresponding (as expected) to destroyed stars clusters, while others (unexpectedly) could plausibly be explained as signatures of resonances with the Galactic bar \citep{dehnen00};
the Sloan Digital Sky Survey \citep[hereafter, SDSS ---][]{york00,stoughton02,abazajian03} found many streams of Main Sequence Turnoff (MSTO) stars in our stellar halo, thought to be from long-dead satellite galaxies and dissolved globular clusters \citep{newberg02,belokurov06} as a stunning confirmation that our Galaxy had indeed formed hierarchically \citep[e.g.][]{bullock01,bullock05};
and M giant stars selected from the Two Micron All Sky Survey \citep[hereafter, 2MASS ---][]{nikolaev00} traced the debris from the Sagittarius dwarf galaxy entirely around the Sky \citep{majewski03} to offer a window on the history of its disruption \citep{law10}.
From these and many other studies that use large survey catalogues, it is now clear that the Milky Way is full of kinematic substructure.

% APW COMMENT: this section makes it sound like the surveys discovered these
% things "for free," but really it was the authors you cite who found these
% things. I would rearrange to say, e.g., "Using data from the
% \survey{Hipparcos} mission \citep{esa97}, moving groups of stars were found
% in the velocity distribution in the Solar Neighborhood
% \citep{dehnen98}...etc"

@@

% APW COMMENT: If the sections are reorganized to be by structure instead,
% this could get moved to the discussion. "Discussion: connections to velocity
% structure near the Sun" or something

@@

% APW COMMENT: If the sections are reorganized to be by structure instead, this
% should be moved to the section on Mon/GASS, I believe

Co-incidental with the above spectroscopic and stellar populations work, \cite{xu15} and \cite{lurie17} explored the spatial distribution of stars in the anticenter region using photometry in the SDSS and PanSTARRS \citep{kaiser10} respectively.
Both employed the novel technique of subtracting color-magnitude diagrams (CMD's) derived from fields in their photometric data which were symmetrically placed at equal and opposite Galactic latitudes and at the same Galactic longitudes.
These differenced CMD's showed sequences in overdensities oscillating between the northern and southern hemispheres as the distance from the Sun was increased towards the anticenter of our Galaxy.
The vast numbers of stars in these surveys allowed more clear identification of the global structures as clearly distinct, separate features.

@@

% APW COMMENT: If you reorganize, I would move the discussion of simulations of
% individual structures to their respective sections about. Instead, I would
% make this section something like "Theoretical interpretations of the global
% structure of the outer disk"

@@

% APW COMMENT: I actually now somewhat disagree with my own cartoon. I will
% think about making a new one that better represents my beliefs about the
% structures. I can also then update this text -- more on that soon!
Figure \ref{fig:cartoon} is a cartoon which summarizes the observational work and its implications, by showing the approximate locations and amplitudes of the spatial and velocity structures that have been identified. (Note that the figure is misleading as the structures are {\it not} consistent morphologically with concentric rings that are axisymmetric about the Galactic center.)
Taken together, we conclude: (i) there is compelling evidence that Mon/GASS, TriAnd I/II and A13 represent populations of stars formed in the disk that now exist at extreme $(R,Z)$;
(ii) that these structures are associated with each other as part of a global system of vertical disk oscillations that can be traced all the way to the velocity asymmetries seen in the Solar Neighborhood; and
(iii) that the stellar populations in these structures are inconsistent with a picture where they formed from an accreted satellite.
